Towards Detecting Stalkerware Through Network Traces

### 2019-03-18 paper/main.tex
Update main.tex
fixed bib

\section{Methodology}
\subsection{Finding Apps}
We selected thirty apps from a list provided by the team of Cornell researchers 
who performed the original large scale study of stalkerware[cite]. An 
additional fifteen apps were included as they were recently added to the app 
store. Apps were chosen for their diversity of purpose and the probability that 
they can be used as stalkerware. These apps are the most likely to be 
downloaded when a abuser without deep technical knowledge tries to install 
stalkerware.

@@

\section{temp}

Some examples.  A paginated journal article \cite{Abril07}, an enumerated 
journal article \cite{Cohen07}, a reference to an entire issue \cite{JCohen96}, 
a monograph (whole book) \cite{Kosiur01}, a monograph/whole book in a series 
(see 2a in spec. document)
\cite{Harel79}, a divisible-book such as an anthology or compilation 
\cite{Editor00} followed by the same example, however we only output the series 
if the volume number is given \cite{Editor00a} (so Editor00a's series should 
NOT be present since it has no vol. no.),
a chapter in a divisible book \cite{Spector90}, a chapter in a divisible book 
in a series \cite{Douglass98}, a multi-volume work as book \cite{Knuth97}, an 
article in a proceedings (of a conference, symposium, workshop for example) 
(paginated proceedings article) \cite{Andler79}, a proceedings article with all 
possible elements \cite{Smith10}, an example of an enumerated proceedings 
article \cite{VanGundy07}, an informally published work \cite{Harel78}, a 
doctoral dissertation \cite{Clarkson85}, a master's thesis: \cite{anisi03}, an 
online document / world wide web resource \cite{Thornburg01, Ablamowicz07, 
Poker06}, a video game (Case 1) \cite{Obama08} and (Case 2) \cite{Novak03} and 
\cite{Lee05} and (Case 3) a patent \cite{JoeScientist001}, work accepted for 
publication \cite{rous08}, 'YYYYb'-test for prolific author \cite{SaeediMEJ10} 
and \cite{SaeediJETC10}. Other cites might contain 'duplicate' DOI and URLs 
(some SIAM articles) \cite{Kirschmer:2010:AEI:1958016.1958018}. Boris / Barbara 
Beeton: multi-volume works as books \cite{MR781536} and \cite{MR781537}. A 
couple of citations with DOIs: 
\cite{2004:ITE:1009386.1010128,Kirschmer:2010:AEI:1958016.1958018}. Online 
citations: \cite{TUGInstmem, Thornburg01, CTANacmart}.

%
% The next two lines define the bibliography style to be used, and the 
%bibliography file.
\bibliographystyle{ACM-Reference-Format}
\bibliography{IPS_Measurement.bib}

>>>>

\section{Methodology}
\subsection{Finding Apps}
We selected thirty apps from a list provided by the team of Cornell researchers 
who performed the original large scale study of stalkerware\cite{chatterjee_spyware_2018}. An 
additional fifteen apps were included as they were recently added to the app 
store. Apps were chosen for their diversity of purpose and the probability that 
they can be used as stalkerware. These apps are the most likely to be 
downloaded when a abuser without deep technical knowledge tries to install 
stalkerware since they are either the first result upon searching for stalkerware, or are well known spyware apps due to advertisement or other reasons.

@@

%
% The next two lines define the bibliography style to be used, and the 
%bibliography file.
\bibliographystyle{ACM-Reference-Format}
\bibliography{IPS_Measurement}
